The core transcriptome of the mammal placenta

### 2016-08-12 manuscript/manuscript.Rnw
change manuscript to use placenta's TeX style

\begin{frontmatter}
\begin{fmbox}
\dochead{Research}%
\title{The evolution of gene expression in the term placenta of viviparous mammals}%
%
\author[addressref={aff1},noteref={n1},email={don@donarmstrong.com}]{\inits{DL}\fnm{Don L} \snm{Armstrong}}
\author[addressref={aff2},noteref={n1},email={1mmcgowen1@gmail.com}]{\inits{MR}\fnm{Michael R.} \snm{McGowen}}
\author[addressref={aff1},email={aweckle@illinois.edu}]{\inits{AL}\fnm{Amy} \snm{Weckle}}
\author[addressref={aff3},email={jacaravas@gmail.com}]{\inits{J}\fnm{Jason} \snm{Caravas}}
\author[addressref={aff4},email={agnewd@dcpah.msu.edu}]{\inits{D}\fnm{Dalen} \snm{Agnew}}
\author[addressref={aff5},email={kbenirschke@ucsd.edu}]{\inits{K}\fnm{Kurt} \snm{Benirschke}}
\author[addressref={aff6},email={suerumbaugh@gmail.com}]{\inits{S}\fnm{Sue} \snm{Savage-Rumbaugh}}
\author[addressref={aff11},email={nevo@research.haifa.ac.il}]{\inits{E}\fnm{Eviatar} \snm{Nevo}}
\author[addressref={aff7,aff8},email={cjkim@med.wayne.edu}]{\inits{CJ}\fnm{Chong J} \snm{Kim}}
\author[addressref={aff9},email={gunter.wagner@yale.edu}]{\inits{GP}\fnm{Günter P.} \snm{Wagner}}
\author[addressref={aff7},email={prbchiefstaff@med.wayne.edu}]{\inits{R}\fnm{Roberto} \snm{Romero}}
\author[addressref={aff1,aff6,aff10},corref={aff1},email={wildmand@illinois.edu}]{\inits{DE}\fnm{Derek E.} \snm{Wildman}}
\address[id=aff1]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff2]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\address[id=aff3]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff4]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\address[id=aff5]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\address[id=aff6]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\address[id=aff7]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\address[id=aff8]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff9]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\address[id=aff10]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff11]{The Institute of Evolution, University of Haifa, Haifa, Israel}

\begin{artnotes}
\end{artnotes}

\begin{artnotes}
\note[id=n1]{Equal contributor} % note, connected to author
\end{artnotes}

\end{fmbox}
% \twocolumn

\begin{abstractbox}
\begin{abstract}
% \section{Abstract}
  \parttitle{Background} The placenta is arguably the most
  anatomically variable organ in mammals. Understanding gene
  expression patterns among placentas from multiple species
  illuminates the molecular basis of placenta function as well
  obstetrical syndromes affecting humans.

  \parttitle{Results} We measured the expression profiles of
  \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals. We
  found lineage-specific differential expression of prolactin,
  relaxin, and galectins as well as increased expression of the
  pre-eclampsia associated genes \textit{ADAM12}, \textit{CRH}, and
  \textit{PAPPA} in humans. We also identified genes which are
  expressed in all placentas, including genes with immune-modulating
  properties (\textit{ANXA2}, \textit{ANXA1}, \textit{S100A11}, and
  \textit{S100A10}) and cell-cell interactions (\textit{LAMC1},
  \textit{LUM}, and \textit{LGALS1}).

>>>>

\title{The core transcriptome of the mammal placenta}%
%
\author[affigb]{Don L. Armstrong\fnref{n1}}
\ead{don@donarmstrong.com}
\author[afflon]{Michael R. McGowen\fnref{n1}}
\ead{1mmcgowen1@gmail.com}
\author[affigb]{Amy Weckle}
\ead{aweckle@illinois.edu}
\author[affwayne]{Jason Caravas}
\ead{jacaravas@gmail.com}
\author[affmich]{Dalen Agnew}
\ead{agnewd@dcpah.msu.edu}
\author[affuscd]{Kurt Benirschke}
\ead{kbenirschke@ucsd.edu}
\author[affapetrust]{Sue Savage-Rumbaugh}
\ead{suerumbaugh@gmail.com}
\author[affhaifa]{Eviatar Nevo}
\ead{nevo@research.haifa.ac.il}
\author[affnih,affwaynepath]{Chong J Kim}
\ead{cjkim@med.wayne.edu}
\author[affyale]{Günter P. Wagner}
\ead{gunter.wagner@yale.edu}
\author[affnih]{Roberto Romero}
\ead{prbchiefstaff@med.wayne.edu}
\author[affigb,affapetrust,affmip]{Derek E. Wildman\corref{cor1}}
\ead{wildmand@illinois.edu}
\cortext[cor1]{Corresponding author}
\address[affigb]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[afflon]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\address[affwayne]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\address[affmich]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\address[affuscd]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\address[affapetrust]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\address[affnih]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\address[affwaynepath]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\address[affyale]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\address[affmip]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[affhaifa]{The Institute of Evolution, University of Haifa, Haifa, Israel}

\begin{abstract}
  \textbf{Background} The placenta is arguably the most
  anatomically variable organ in mammals.

  \textbf{Results} We measured the expression profiles of
  \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals. We
  found lineage-specific differential expression of prolactin,
  relaxin, and galectins as well as increased expression of the
  pre-eclampsia associated genes \textit{ADAM12}, \textit{CRH}, and
  \textit{PAPPA} in humans. We also identified genes which are
  expressed in all placentas, including genes with immune-modulating
  properties (\textit{ANXA2}, \textit{ANXA1}, \textit{S100A11}, and
  \textit{S100A10}) and cell-cell interactions (\textit{LAMC1},
  \textit{LUM}, and \textit{LGALS1}).
